---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  error = TRUE
)
```

# fortunes

<!-- badges: start -->
<!-- badges: end -->

The goal of fortunes is for the user to select three words out of the provided selections and then receive a fortune. 

## Installation

You can install the development version of fortunes from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("TanishaChetty/fortunes")
```

## Usage

When using the `fortunes()` function an argument is unneeded, but is an option! Without an argument, the function will give you three prompts one after another in which you will select a word out of those provided for both of them. Make note that it is case sensitive. From there, the function will give you a fortune from the built-in data set `fortunes`. All you need to do to properly run the function is shown below:

```{r example}
library(fortunes)
fortunes()
```

If you wish to choose the words from the lists and put them into the argument yourself you can do the following:

```{r}
library(fortunes)
fortunes(fortuney_words = "luck", awesome_words = "sparkle", evil_words = "brimstone")
```

