---
title: "Using the fortunes package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the fortunes package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = TRUE
)
```

## Fortune Telling

The main function of the fortunes package is to provide a fortune to the user after asking them to choose a few words! Or they can choose three words themselves to get a fortune by putting them in the argument. To start, we must first load the `fortunes` package.

```{r setup}
library(fortunes)
```

When you use the `fortunes()` function, you will be shown three different prompts that will ask you to choose from a set of provided words. You have to match the word completely including case and spelling. The function will then provide a fortune based on the final word you have chosen. It does this by seeing if your word's length divided by two's remainder is equal to zero or not and then assigning a certain range of the data set that it will randomly choose a fortune string from. 

```{r}
fortunes()
```

The alternative method is to select three words yourself. The function will use your last word's length divided by two's remainder and based on if it is equal to zero or not and then assigning a certain part of the data set that it will randomly choose a fortune string from. Overall, it's very similar to the above method. For example, lets use the words lucky, rad, and naughty!

```{r}
fortune(fortuney_words = "lucky", awesome_words = "rad", evil_words = "naughty")
```


## Fortunes Data 

The fortunes package comes with the fortunes data. We use this data within the fortunes() function to assign you a fortune! However, you can also access this data yourself if you wish to use it. It contains 50 different fortunes from the website http://www.fortunecookiemessage.com/archive.php?start=0.
