---
title: "Using the fortunes package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the fortunes package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Fortune Telling

The main function of the fortunes package is to provide a fortune to the user after asking them to choose a few words! To start, we must first load the `fortunes` package.

```{r setup}
library(fortunes)
```

When you use the `fortunes()` function to be shown the two different prompts that will ask you to choose from a set of provided words. You have to match the word completely including case and spelling. The function will then provide a fortune based on the final word you have chosen. It does this by seeing if your remainder is equal to zero or not and then assigning a certain part of the data set that it will randomly choose a fortune string from. 

```{r}
fortunes()
```

## Fortunes Data 

The fortunes package comes with the fortunes data. We use this data within the fortunes() function to assign you a fortune! However, you can also access this data yourself if you wish to use it. It contains 50 different fortunes from the website http://www.fortunecookiemessage.com/archive.php?start=0.
